Investigating the alternative prey hypothesis with the POMP framework

### 2024-04-22 draft.Rmd
minor change

```{r libraries, echo=FALSE, message=FALSE}
library(readxl)
library(ggplot2)
library(knitr)
library(forecast)
library(dplyr)
library(cowplot)
library(pomp)
```

```{r data_table, echo=FALSE}
data <- read_excel("./data/bird_data.xlsx")
data |>
  rename(peak_rodent_year = "peak rodent year") |>
  rename(NAO = "NAO May_Jun_Jul")-> data

knitr::kable(data[1:5, 1:7], caption = "Data")
```

>>>>

```{r libraries, echo=FALSE, message=FALSE, warning=FALSE}
library(readxl)
library(ggplot2)
library(knitr)
library(forecast)
library(dplyr)
library(cowplot)
#library(pomp)
```

```{r data_table, echo=FALSE}
data <- read_excel("./data/bird_data.xlsx")
data |>
  rename(peak_rodent_year = "peak rodent year") |>
  rename(NAO = "NAO May_Jun_Jul") |>
  select(c(year, CPUE, peak_rodent_year, NAO)) -> data

knitr::kable(data, caption = "Data")
```
